X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2014-03-04 hedpc.tex
typo + white G012 in fig 2

Possible usages of edge-on grating interferometry encompasse applications
ranging from medical imaging to non-destructive testing and homeland
security. All these applications seek for high (greater than
\SI{100}{\kilo\eV}) nominal energies
and compact designs. Particularly for medical application, the operation of
a phase contrast imaging device at high energies is imperative. When imaging
patients, a crucial issue is the dose, which depends mainly on the
absorption of the X-rays and decreases with the third power of the photon
energy~\cite{Momose2005}. On the other hand, the phase interaction is only inversely
proportional to the energy and is therefore relatively much more relevant
than absorption as the energy increases, possibly leading to a decreased
exposure for an equivalent image quality. Clinical operation of such a
device will imply measuring patients who normally breath, move and shake.
Fast acquisitions are therefore required, in order to keep the images sharp
and artefact free. As a consequence, compact, efficient imaging systems need
to be developed to provide imaging capabilities at sufficient speed. Our
circular grating alignment matches the structures of the diffracting and
absorbing elements to the divergent beam, especially for compact geometries.
In conclusion, short, high-energy phase-contrast systems will enable the
efficient investigation of high-density materials or thick samples, adding
information on electron density and integrated small-angle scattering power
to the conventional absorption-based signal. This will improve material
discrimination and density sensitivity in future X-ray or even
neutron~\cite{Grunzweig2008} investigations.

>>>>

Possible usages of edge-on grating interferometry encompass applications
ranging from medical imaging to non-destructive testing and homeland
security. All these applications seek for high (greater than
\SI{100}{\kilo\eV}) nominal energies
and compact designs. Particularly for medical application, the operation of
a phase contrast imaging device at high energies is imperative. When imaging
patients, a crucial issue is the dose, which depends mainly on the
absorption of the X-rays and decreases with the third power of the photon
energy~\cite{Momose2005}. On the other hand, the phase interaction is only inversely
proportional to the energy and is therefore relatively much more relevant
than absorption as the energy increases, possibly leading to a decreased
exposure for an equivalent image quality. Clinical operation of such a
device will imply measuring patients who normally breath, move and shake.
Fast acquisitions are therefore required, in order to keep the images sharp
and artefact free. As a consequence, compact, efficient imaging systems need
to be developed to provide imaging capabilities at sufficient speed. Our
circular grating alignment matches the structures of the diffracting and
absorbing elements to the divergent beam, especially for compact geometries.
In conclusion, short, high-energy phase-contrast systems will enable the
efficient investigation of high-density materials or thick samples, adding
information on electron density and integrated small-angle scattering power
to the conventional absorption-based signal. This will improve material
discrimination and density sensitivity in future X-ray or even
neutron~\cite{Grunzweig2008} investigations.
